Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA

### 2022-08-18 src/tex/ms.tex
updated text, added more to table, fixed chirp mass figure

\textbf{The transition between individually resolved DWDs and the confusion limited, or unresolved, DWD foreground is expected to occur near $\sim1\,\rm{mHz}$ frequencies \citep[e.g. ][]{Ruiter2010}. In the confusion limited regime, more than one binary radiates GWs in each LISA frequency bin, thus creating a superposition of signals which are unable to be disentangled. There are multiple parameters which shape the Galactic DWD foreground. Assuming the evolution of each DWD system is driven solely by GW emission, the frequency derivative scales proportionally to $f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies \citep{Breivik2019fg}. The spatial density of DWDs in the Galaxy  which defines the distance to each binary also impacts the foreground amplitude, since strain scales inversely with distance. Star formation history assumptions combine these two effects by assigning ages and positions to each DWD in the population which determine the present day orbital (and thus GW) frequencies as well as distances to each source.}

@@

%\subsection{The metallicity-dependent binary fraction}
To date, population synthesis studies of the Galactic population of close DWDs have either assumed a $100\%$ binary fraction or a $50\%$ binary fraction, such that for every three stars formed, two reside in a binary system \citep{Nelemans2001a, Yu2013, Korol2017, Lamberts2019}. In this study, we investigate the effects of a metallicity-dependent binary fraction on the formation and evolution of DWDs. To this end, we create synthetic present-day Milky Way-like galaxies of DWDs and specifically select systems with GW signals that may be observable by the space-based detector LISA. Throughout, we make comparisons between the standard assumption of a constant $50\%$ initial binary fraction (hereafter model F50) and one with a metallicity-dependent binary fraction (hereafter model FZ).

In Section \ref{sec:simulations} we discuss our binary evolution assumptions used in simulating DWD populations and detail the process to produce present-day synthetic Milky-Way-like galaxies. In Section \ref{sec:LISA_obs} we review the derivation of LISA detectability for circular DWD populations at mHz frequencies. In Section \ref{sec:results} we detail results showing how a metallicity-dependent binary fraction affects the formation and evolution of DWD populations assuming a fiducial set of binary evolution assumptions. In Section \ref{sec:LISA_met} we detail the metallicity dependence of the LISA DWD foreground and resolved population. Finally, we repeat our analysis for three sets of binary evolution assumptions to show a robust reduction of the size of the Galactic DWD foreground in LISA for populations simulated with a metallicity-dependent binary fraction in Section \ref{sec:model_compare} and conclude in Section \ref{sec:conclusions}.

@@

The masses and orbital periods at the formation of the second-formed WD span a wide range depending on the WD binary component types, thus we consider four DWD combinations: two helium WDs (He + He), a carbon-oxygen WD orbiting a helium WD (CO + He), two carbon-oxygen WDs (CO + CO), and an oxygen-neon orbiting a helium, carbon-oxygen, or oxygen-neon WD (ONe + X). For each DWD type we simulate a grid of $15$ metallicities spaced uniformly in $\log_{10}(Z)$ between $Z=10^{-4}$ to $0.03$, to account for the limits of the \citet{Hurley2000} stellar evolution tracks employed in \cosmic. This results in a total of $60$ populations across all DWD types and metallicities. The output of \cosmic\ contains information limited to intrinsic binary properties like mass and orbital period. External parameters like Galactic position and orientation are assigned in a post-processing scheme which uses metallicity-dependent positions and ages from the Ananke framework of galaxy \textbf{m12i} from the Latte Suite of the FIRE-2 simulations (see Section~\ref{sec:FIRE} for details).

We assume that the Zero Age Main Sequence (ZAMS) masses, orbital periods and eccentricities for each binary are independently distributed. We choose primary masses following \citet{Kroupa2001}, a flat mass ratio distribution \citep{Mazeh1992, Goldberg1994}, a log-uniform period distribution following Opik's Law, and a uniform eccentricity distribution following \cite{Geller2019}. We initialize all binaries with the same evolution time of $13.7\,\rm{Gyr}$ to capture all potential evolution within a Hubble time. We assume a $100\%$ binary fraction in our COSMIC simulations to reduce computation time and scale the simulations to models which assume a constant $50\%$ binary fraction (model F50) or a metallicity-dependent binary fraction (model FZ) in a post-processing scheme.

Since we are primarily interested in the effects of a metallicity-dependent binary fraction, we use a single set of assumptions for binary interactions. Our choices follow the \texttt{COSMIC} defaults described in \citet{Breivik2020a} except for the treatment of Roche-lobe overflow (RLO). The stability of RLO mass transfer is determined using critical mass ratios resulting from radius-mass exponents \citep{Webbink1985, Hurley2002}, where the critical mass ratio is defined as the ratio of the donor to accretor mass. We assume critical mass ratios following \citet{Claeys2014} which reduce the standard critical mass ratio assumptions from \citet{Hurley2002} for main sequence (MS) donors by $\sim50\%$ from $3$ to $1.6$ based on the models of \citet{deMink2007} and treat WD accretors separately following the models of \citet{Soberman1997}. We increase the mass loss rate from the donor following Equation 11 of \citet{Claeys2014}. The amount of mass lost during RLO from the donor is limited by the overflow factor of the donor radius to its Roche radius following \citet{Hurley2002}. The amount of mass accepted by the accretor is limited to $10$ times the accretor's mass divided by the accretor's thermal timescale. Finally, for RLO mass loss which becomes unstable and leads to common envelope evolution (CEE) we assume that the donor's binding energy is calculated according to the fits detailed in Appendix B of \citet{Claeys2014} and that orbital energy is deposited with $100\%$ efficiency into unbinding the common envelope ($\alpha=1$).

\subsection{Metallicity-dependent binary fraction}
We fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and binary fraction $f_{\rm{b}}$ as

\[f_{\rm{b}}= \begin{cases} 
      - 0.0648 \cdot [\rm{Fe/H}] + 0.3356, & [\rm{Fe/H}]\leq -1.0 \numberthis \\
      -0.1977 \cdot [\rm{Fe/H}] + 0.2025, & [\rm{Fe/H}]> -1.0  
   \end{cases}
\]

\noindent We convert between [Fe/H] and metallicity Z, assuming all stars have solar abundance such that
\begin{equation}
\label{eq:metallicity}
    [\rm{Fe/H}] = \log_{10}\Big(\frac{Z}{Z_{\odot}}\Big),
\end{equation}
\noindent where we assume $Z_{\odot}=0.02$.

\subsection{A metallicity-dependent SFH: Convolving with the FIRE-2 models}
\label{sec:FIRE}
To create Milky Way-like galaxies which integrate the metallicity-dependent binary fraction, we use the metallicity-dependent ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the FIRE-2 simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create synthetic, Milky Way-like DWD populations.

@@

The metallicity-dependent binary fraction is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid. The binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly. These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.

Since our \cosmic\ simulations assume a binary fraction of $f_{\rm{b}} = 1$, we scale the amount of mass sampled at ZAMS required to produce our \cosmic-generated population of DWDs ($M_{\text{b,ZAMS}}$) to the proper amount of mass sampled in single and binary stars ($M_{\text{ZAMS,sim}}$) for each binary fraction and model. We do this by sampling single stars and primary masses of binary stars from the \cite{Kroupa2001} IMF and sampling secondary masses of the binary stars from a uniform mass distribution, where the number of binaries is determined by the binary fraction model (F50 or FZ). From this sample, we obtain the ratio of mass in single stars to the mass in binary stars as a function of the binary fraction, $R(f_{\rm{b}})$. For model F50, the ratio is a constant $R(f_{\rm{b}}) = 0.64$. For model FZ, the ratio increases from 0.68 at low metallicities to 3.17 at solar metallicity indicating less mass in binaries relative to single stars. The total amount of ZAMS mass in single and binary stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + R(f_{\rm{b}}))$.

@@

We discard any DWDs for which the sum of their ZAMS birth time, given by the star particle formation time, and DWD formation time is larger than the age of the star particle since the system will not have evolved long enough to become a DWD at present. We further discard any DWDs for which the lower mass WD overflows it's Roche lobe before present day, because the outcomes of these interactions are highly uncertain and their treatment is outside the scope of this work \citep[e.g., ][]{Shen2015, Kremer2017}. \textbf{We also note that stably accreting WD binaries are unlikely to contribute appreciably to the Galactic DWD foreground due to their small mass ratios at frequencies below $1\,\rm{mHz}$ \citep{Breivik2018}.} The separation at which the lower mass WD overflows its Roche Lobe is defined as

@@

\begin{table}[]
    \centering
    \begin{tabular}{|c|c|c|c|c|c|}
       \hline
       model & a & b & c & d & e \\
       \hline
       \hline
       F50 & -223.5 & -189.8 & -76.8 & -14.0 & -1.0 \\
       \hline
       FZ & -558.5 & -575.4 & -243.1 & -45.8 & -3.2 \\
       \hline
    \end{tabular}
    \caption{Polynomial fitting coefficients for the confusion foreground fit of Equation~\ref{eq:fit} for each binary fraction model.}
    \label{tbl:fits}
\end{table}

@@

\subsection{Metallicity-dependent trends in the formation efficiency of DWDs}\label{sec:formeff}
The number of DWDs formed per unit solar mass of ZAMS star formation, or DWD formation efficiency $\eta_{\rm{form}}(Z))$, varies with metallicity. Consequently, a metallicity-dependent binary fraction further impacts the efficiency of DWD formation within the Galaxy. Figure \ref{fig:form_eff} shows the DWD formation efficiency as a function of metallicity for each DWD type and for each of our binary fraction models. In general, the formation efficiency decreases with increasing metallicity. This effect is exaggerated for model FZ which assumes a binary fraction which also decreases with increasing metallicity.

For He + He DWDs, the sudden drop in formation efficiency near $\log(Z/Z_{\odot})=-1.0$, is generally caused by the timescale for which the initially more massive star in the DWD progenitor overflows it's Roche lobe. At lower metallicities, donors tend to fill their Roche lobes while they are still on the main sequence and the mass transfer remains stable. This is because, in our \cosmic\ models lower metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS. At higher metallicities, mass transfer is initiated when the donor has left the main sequence and the binary enters a common envelope evolution. The ZAMS orbital period leads to different specific evolutionary channels. For short-period systems with periods below $10~\rm{days}$, this leads to a stellar merger due to insufficient orbital energy to eject the envelope. Stellar mergers continue to dominate the evolutionary pathways of systems with intermediate orbital periods ($1 < \log_{10}(P_{\rm{orb}}/\rm{day}) < 2.5$). However, an additional growing number of merging systems arises with one WD component and one stellar companion, and systems which don't interact at all and thus do not form a He + He DWD. The distinction between the various scenarios in this intermediate orbital period range depends on the combination of their ZAMS masses and orbital periods. Finally, at wider initial periods $\log_{10}(\rm{P}) > 2.5$, the decrease in formation efficiency is dominated by systems which never interact and thus do not form a DWD before the present day.

@@

For short-period CO + He DWD progenitor binaries with orbital periods below $\sim30~\rm{days}$, the only channel for mergers before DWD formation is during a CE evolution. This channel is similar to the stellar merger channel for He + He DWDs, but due to higher-mass progenitors the CE evolution results in the binary component with a higher mass becoming a CO WD. At higher metallicities, the CO WD merges with its companion. Higher-metallicity progenitors have a larger fraction of their mass in the convective envelope when compared to lower-metallicity stars of the same mass \citep{Amard2019, Amard2020} Thus a CE phase with a higher-metallicity progenitor requires more orbital energy to eject the common envelope, causing a larger amount of orbital shrinking which results in a merger later in its binary evolution.

@@

Long-period binaries with $\log_{10}(P_{\rm{orb}}/\rm{day})>2.5$ also display complex scenarios that hinder CO + He DWD formation. In near-equal contributions, our \cosmic\ simulations produce either stellar mergers or stable non-DWD binaries at the end of the Hubble time. At these orbital periods, stellar mergers always occur with a CE phase between a stellar companion and a CO or He WD. Similar to binaries with shorter orbital periods, the mergers occur because of increased CE donor envelope masses at higher metallicities. A subdominant channel of stable He + He DWDs can also occur when a high-metallicity primary overflows it's Roche lobe while still on the GB and thus forms a He WD.

@@

@@

Figure \ref{fig:CEsep} shows the average separation at the first instance of CE evolution, $a_{\text{CE}}$ of all DWD progenitors that result in systems orbiting in the LISA frequency band at present day, as a function of metallicity for each DWD type. The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading. The average CE separation increases in general across metallicity. Higher-metallicity binaries will interact earlier in the binary's lifetime than a lower-metallicity binary of equal separation due to their relatively larger maximum radii. Since higher-metallicity binaries are also more likely to merge during CE interactions because of their relatively more massive donor envelopes, the DWDs which survive and eventually orbit in the LISA band originate from systems with higher interaction separations which allow their orbits to shrink significantly during CE phases without merging. This regulation plays a key role in smearing out any observable effects of a metallicity-dependent binary fraction in the population of DWDs observable by LISA.

>>>>

%I did some switching around of words
\textbf{The transition between individually resolved DWDs and the confusion limited, or unresolved, DWD foreground is expected to occur near $\sim1\,\rm{mHz}$ frequencies \citep[e.g. ][]{Ruiter2010}. In the confusion limited regime, more than one binary radiates GWs in each LISA frequency bin, thus creating a superposition of signals which are unable to be disentangled. There are multiple parameters which shape the Galactic DWD foreground. Assuming the evolution of each DWD system is driven solely by GW emission, the frequency derivative scales proportionally to $f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies \citep[e.g.][]{Breivik2020b}. The spatial density of DWDs in the Galaxy which defines the distance to each binary also impacts the foreground amplitude, since GW strain scales inversely with distance. Star formation history assumptions combine these two effects by assigning ages and positions to each DWD in the population which determine the present day orbital (and thus GW) frequencies as well as distances to each source.}

%\textbf{There also exists a ``transition" GW frequency at which the GW spectrum transitions from confusion limited to being able to detect individual sources \citep{Ruiter2010}. In the confusion-limited regime, greater than one binary exists per LISA frequency bin, creating a superposition of signals which are unable to be disentangled. There are multiple parameters which serve to shape the Galactic DWD foreground. Assuming the evolution of each DWD system is driven solely by GW emission, the frequency derivative scales proportionally to $f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies \citep{Breivik2019fg}. The distance dependence of the spatial density of DWDs in the Galaxy also impacts the foreground amplitude, since strain scales inversely with distance. Star formation history assumptions impact the foreground height, as the duration of GW orbital evolution of each system will impact contributions to strain.}

@@

To date, population synthesis studies of the Galactic population of close DWDs have either assumed a $100\%$ binary fraction or a $50\%$ binary fraction, such that for every three stars formed, two reside in a binary system \citep{Nelemans2001a, Yu2013, Korol2017, Lamberts2019}. In this study, we investigate the effects of a metallicity-dependent binary fraction on the formation and evolution of DWDs. To this end, we create synthetic present-day Milky Way-like galaxies of DWDs and specifically select systems with GW signals that may be observable by the space-based detector LISA. Throughout, we make comparisons between the standard assumption of a constant $50\%$ initial binary fraction (hereafter model F50) and one with a metallicity-dependent binary fraction (hereafter model FZ).

In Section \ref{sec:simulations} we discuss our %binary evolution KB commented out
assumptions used in simulating DWD populations and detail the process to produce present-day synthetic Milky-Way-like galaxies. In Section \ref{sec:LISA_obs} we review the derivation of LISA detectability for circular DWD populations at mHz frequencies. In Section \ref{sec:results} we detail results showing how a metallicity-dependent binary fraction affects the formation and evolution of DWD populations assuming \kb{\sout{a fiducial set} four sets of} of binary evolution assumptions. In Section \ref{sec:LISA_met} we detail the metallicity dependence of the LISA DWD foreground and resolved population. Finally, \kb{\sout{we repeat our analysis for three sets of binary evolution assumptions  to show a robust reduction of the size} we consider how a metallicity-dependent close binary fraction impacts the height} of the Galactic DWD foreground in LISA for \kb{\sout{populations simulated with a metallicity-dependent binary fraction} different binary evolution assumptions} in Section \ref{sec:model_compare} and conclude in Section \ref{sec:conclusions}.

@@

The masses and orbital periods at the formation of the second-formed WD span a wide range depending on the WD binary component types, thus we consider four DWD combinations: two helium WDs (He + He), a carbon-oxygen WD orbiting a helium WD (CO + He), two carbon-oxygen WDs (CO + CO), and an oxygen-neon orbiting a helium, carbon-oxygen, or oxygen-neon WD (ONe + X). For each DWD type we simulate a grid of $15$ metallicities spaced uniformly in $\log_{10}(Z)$ between $Z=10^{-4}$ to $0.03$, to account for the limits of the \citet{Hurley2000} stellar evolution tracks employed in \cosmic. This results in a total of $60$ populations across all DWD types and metallicities \kb{for each set of model assumptions}. The output of \cosmic\ contains information limited to intrinsic binary properties like mass and orbital period. External parameters like Galactic position and orientation are assigned in a post-processing scheme which uses metallicity-dependent positions and ages from the Ananke framework of galaxy \textbf{m12i} from the Latte Suite of the FIRE-2 simulations (see Section~\ref{sec:FIRE} for details).

We assume that the Zero Age Main Sequence (ZAMS) masses, orbital periods and eccentricities for each binary are independently distributed. We choose primary masses following \citet{Kroupa2001}, a flat mass ratio distribution \citep{Mazeh1992, Goldberg1994} and a uniform eccentricity distribution following \cite{Geller2019}. \snotes{For our simulations which follow a metallicity-dependent binary fraction (model FZ), a skewed log-normal orbital period distribution is sampled in accordance with the metallicity-dependent companion frequency of \citet{Moe2021} \kb{\sout{which will be} as} discussed in Section \ref{subsec:metbinfrac}.} 
%\kb{Binaries are then assigned orbital periods by sampling from this distribution. As will be discussed below, when this distribution is integrated it results in the binaries having the binary fraction associated with that metallicity. } I cut this since I think it's covered above now!
%\kb{For all FZ simulations, we only retain the binary systems and discard single stars, but save information regarding how much mass in stars is required to create each population for incorporating a metallicity-dependent star formation history as will be discussed in Section \ref{sec:FIRE}. } I also don't think we need this info
\snotes{For our simulations which assume a constant 50\% binary fraction (model F50), we use a log-uniform period distribution following Opik's Law similar to previous studies \citep[e.g.][]{Nelemans2001a, Toonen2012, Korol2017, Lamberts2019}. We assume a $100\%$ binary fraction in the F50 COSMIC simulations to reduce computation time and scale the simulations to a constant $50\%$ binary fraction in a post-processing scheme.} We initialize all binaries with the same evolution time of $13.7\,\rm{Gyr}$ to capture all potential evolution within a Hubble time. \snotes{Although we simulate binaries across the full orbital period distribution, we discard \kb{DWD} binaries \kb{which form} with separations $a\geq 1000$ R$_\odot$ during post-processing, \kb{\sout{to save on computational work}} since these are unlikely to evolve into the LISA band by present day.}

\kb{We consider a fiducial set of assumptions which } follow the \texttt{COSMIC} defaults described in \citet{Breivik2020a} except for the treatment of Roche-lobe overflow (RLO). The stability of RLO mass transfer is determined using critical mass ratios resulting from radius-mass exponents \citep{Webbink1985, Hurley2002}, where the critical mass ratio is defined as the ratio of the donor to accretor mass. We assume critical mass ratios following \citet{Claeys2014} which reduce the standard critical mass ratio assumptions from \citet{Hurley2002} for main sequence (MS) donors by $\sim50\%$ from $3$ to $1.6$ based on the models of \citet{deMink2007} and treat WD accretors separately following the models of \citet{Soberman1997}. We increase the mass loss rate from the donor following Equation 11 of \citet{Claeys2014}. The amount of mass lost during RLO from the donor is limited by the overflow factor of the donor radius to its Roche radius following \citet{Hurley2002}. The amount of mass accepted by the accretor is limited to $10$ times the accretor's mass divided by the accretor's thermal timescale. Finally, for RLO mass loss which becomes unstable and leads to common envelope evolution (CEE) we assume that the donor's binding energy is calculated according to the fits detailed in Appendix B of \citet{Claeys2014} and that orbital energy is deposited with $100\%$ efficiency into unbinding the common envelope ($\alpha=1$).

\snotes{The LISA-detectable DWD populations that result from our simulations may vary depending on the assumptions made regarding binary interactions. In order to explore the range of results, we complete this study for three binary evolution parameter variations on top of our fiducial set of assumptions. For each variation, we consider models FZ and F50 as done in the fiducial case described above. In variation $q3$, we vary the assumption for the critical mass ratios at which a RLO interaction remains stable or becomes unstable from our fiducial assumptions such that the critical mass ratio is increased to $3.0$ and thus allows stable mass transfer for more massive RLO donors. In variations $\alpha25$ and $\alpha5$, we modify the common envelope ejection efficiency to be either much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial assumption ($\alpha=1$). Larger common envelope ejection efficiencies lead to wider post-CE separations, while smaller ejection efficiencies either lead to closer post-CE separations or \kb{stellar} mergers where the envelope ejection fails. \kb{\sout{This will be discussed further later on.}} Between all variations, all other prescriptions for binary evolution remain identical besides the one varied parameter. We delve in depth into the fiducial results in each section, and then give a brief overview of how the results change for each parameter variation.}

\subsection{A metallicity-dependent SFH: Convolving with the FIRE-2 models}
\label{sec:FIRE}
To create Milky-Way-like galaxies which integrate the metallicity-dependent binary fraction, we use the metallicity-dependent ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the FIRE-2 simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create synthetic, Milky-Way-like DWD populations.

@@

The metallicity-dependent \kb{close} binary fraction \snotes{for \kb{\sout{close, }}solar-type binaries (P $< 10^4$ days), or simply the \kb{close} binary fraction from here on,} is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid. The binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly. These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.

Since our \cosmic\ simulations assume a binary fraction of $f_{\rm{b}} = 1$ \snotes{for model F50}, we scale the amount of mass sampled at ZAMS required to produce our \cosmic-generated population of DWDs ($M_{\text{b,ZAMS}}$) to the proper amount of mass sampled in single and binary stars ($M_{\text{ZAMS,sim}}$). We do this by sampling single stars and primary masses of binary stars from the \cite{Kroupa2001} IMF and sampling secondary masses of the binary stars from a uniform mass distribution, where the number of binaries is calculated to ensure $f_{\rm{b}}=0.5$. From this sample, we obtain the ratio of mass in single stars to the mass in binary stars, $R(f_{\rm{b}})$. For model F50, the ratio is a constant $R(f_{\rm{b}}) = 0.64$. \snotes{The total amount of ZAMS mass in single and binary stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + R(f_{\rm{b}}))$. For model FZ, no scaling is done since the \cosmic\ simulations already have the binary fraction incorporated, so $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}}$}.

@@

We discard any DWDs for which the sum of their ZAMS birth time, given by the star particle formation time, and DWD formation time is larger than the age of the star particle since the system will not have evolved long enough to become a DWD at present. We further discard any DWDs for which the lower mass WD overflows it's Roche lobe before present day, because the outcomes of these interactions are highly uncertain and their treatment is outside the scope of this work \citep[e.g., ][]{Shen2015, Kremer2017}. \textbf{This choice does not significantly affect our results since stably accreting WD binaries are unlikely to contribute appreciably to the Galactic DWD foreground due to their small mass ratios at frequencies below 1 mHz \citep{Breivik2018}.} The separation at which the lower mass WD overflows its Roche Lobe is defined as

@@

\begin{table}[]
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|}
       \hline
       parameter variation & model & a & b & c & d & e \\
       \hline
       \hline
       fiducial & F50 & -217.8 & -183.9 & -74.5 & -13.7 & -0.94452821 \\
       \hline
       fiducial & FZ & -268.2 & -243.0 & -100.5 & -18.7 & -1.3 \\
       \hline
       $\alpha25$ & F50 & -5520.2 & -6078.3 & -2528.8 & -467.1 & -32.3 \\
       \hline
       $\alpha25$ & FZ & -2816.0 & -3066.4 & -1272.7 & -234.7 & -16.2 \\
       \hline
       $\alpha5$ & F50 & -178.7 & -142.8 & -58.7 & -11.0 & -0.8 \\
       \hline
       $\alpha5$ & FZ & -265.9 & -239.8 & -99.1 & -18.5 & -1.3 \\
       \hline
       q3 & F50 & -114.5 & -73.5 & -30.9 & -6.1 & -0.5 \\
       \hline
       q3 & FZ & -336.9 & -323.5 & -136.2 & -25.8 & -1.8 \\
       \hline
    \end{tabular}
    \caption{Polynomial fitting coefficients for the confusion foreground fit of Equation~\ref{eq:fit} for each binary fraction model.}
    \label{tbl:fits}
\end{table}

@@

\subsection{Metallicity-dependent trends in the formation efficiency of DWDs}\label{sec:formeff}
The number of DWDs formed per unit solar mass of ZAMS star formation, or DWD formation efficiency $\eta_{\rm{form}}(Z)$, varies with metallicity. Consequently, a metallicity-dependent binary fraction further impacts the efficiency of DWD formation within the Galaxy. Figure \ref{fig:form_eff} shows the DWD formation efficiency as a function of metallicity for each DWD type\snotes{,\sout{ and for each of our}} binary fraction models\snotes{, and binary evolution parameter variations}. In general, the formation efficiency decreases with increasing metallicity. This effect is exaggerated for model FZ which assumes a binary fraction which also decreases with increasing metallicity.

\subsubsection{\snotes{Fiducial formation efficiency trends}}\label{sec:formeff_fid}

For He + He DWDs, the sudden drop in formation efficiency near $\log(Z/Z_{\odot})=-1.0$, is generally caused by the timescale for which the initially more massive star in the DWD progenitor overflows it's Roche lobe. At lower metallicities, donors tend to fill their Roche lobes while they are still on the main sequence and the mass transfer remains stable \snotes{and serves to widen the binary}. This is because, in our \cosmic\ models lower metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS. At higher metallicities, mass transfer is initiated when the donor has left the main sequence, and the binary enters a common envelope evolution. The ZAMS orbital period leads to different specific evolutionary channels. For short-period systems with periods below $10~\rm{days}$, this leads to a stellar merger due to insufficient orbital energy to eject the envelope. Stellar mergers continue to dominate the evolutionary pathways of systems with intermediate orbital periods ($1 < \log_{10}(P_{\rm{orb}}/\rm{day}) < 2.5$). However, an additional growing number of merging systems arises with one WD component and one stellar companion, and systems which don't interact at all and thus do not form a He + He DWD. The distinction between the various scenarios in this intermediate orbital period range depends on the combination of their ZAMS masses and orbital periods. Finally, at wider initial periods $\log_{10}(\rm{P}) > 2.5$, the decrease in formation efficiency is dominated by systems which never interact and thus do not form a DWD before the present day.

@@

For short-period CO + He DWD progenitor binaries with orbital periods below $\sim30~\rm{days}$, the only channel for mergers before DWD formation is during a CE evolution. This channel is similar to the stellar merger channel for He + He DWDs, but due to higher-mass progenitors the CE evolution results in the binary component with a higher mass becoming a CO WD. At higher metallicities, the CO WD merges with its companion. Higher-metallicity progenitors have a larger fraction of their mass in the convective envelope when compared to lower-metallicity stars of the same mass \citep{Amard2019, Amard2020}. Thus a CE phase with a higher-metallicity progenitor requires more orbital energy to eject the common envelope, causing a larger amount of orbital shrinking which results in a merger later in its binary evolution.

@@

Long-period binaries with $\log_{10}(P_{\rm{orb}}/\rm{day})>2.5$ also display complex scenarios that hinder CO + He DWD formation. In near-equal contributions, our \cosmic\ simulations produce either stellar mergers or stable non-DWD binaries at the end of the Hubble time. At these orbital periods, stellar mergers always occur with a CE phase between a stellar companion and a CO or He WD. Similar to binaries with shorter orbital periods, the mergers occur because of increased CE donor envelope masses at higher metallicities. A subdominant channel of stable He + He DWDs can also occur when a high-metallicity primary overflows it's Roche lobe while still on the GB and thus forms a He WD. \snotes{In general, a CO + He binaries fails to form because either a CO + CO or He + He is formed isntead, or a merger occurs before DWD formation. We see higher efficiency for FZ than F50 because Co + He binaries prefer to form in log$_{10}$(P$_{\rm{orb}}$/day)$\sim2-4$, which is where the orbital period distribution of FZ peaks.}

@@

\subsubsection{\snotes{Parameter variations formation efficiency trends}}\label{subsec:formeff_vars}

\snotes{For our simulations with parameter variations, we see an interplay of the physics of binary evolution with the skews introduced by the metallicity-dependent orbital period distribution/binary fraction. We will summarize how the formation efficiency of each DWD type is impacted by the parameter variations. Of note in this analysis is that a) the log-normal metallicity-dependent ZAMS orbital period distribution increasingly skews towards orbital periods below $10^4$ days for decreasing metallicity. However, b) the log-uniform P$_{\rm{orb}}$ distribution of F50 produces a higher number of the shortest orbital period systems (below $\sim 100$ days) than for FZ as the tails of the FZ distribution fall quickly below this threshold.}

\snotes{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial simulations. The lower CE efficiency entails mergers from the binary failing to eject the CE, or shrinking the orbit such that it then merges on the second CE phase. Because, as discussed above, there are more very short-period binaries in F50, as the ZAMS binary population evolves there are more likely to be binary interactions in the population for F50 than FZ. This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD and thus a lower formation efficiency overall for F50 in contrast to FZ, as we see in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}. Similarly to the fiducial, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales. These later interactions lead to closer post-CE separations and thus more mergers. The dip at [Fe/H]=$\sim -1.5\%$ stems from mergers before the DWD forms, similar to for our fiducial model. The  peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster (i.e. interacting earlier) as metallicity increases, meaning that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive into an He + He. At higher metallicities, there are a higher proportion of wide-separation systems, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop. For $\alpha5$, there are significantly fewer mergers, as expected since binaries are more likely to survive a CE phase from the higher CE efficiency. Systems that would normally merge for $\alpha25$ now survive, and are shrunk to short orbits through CE interactions to evolve in the LISA band. The number of DWDs thus makes up a higher fraction of the total simulated binary population overall, thus we see in general higher formation efficiencies than for our fiducial simulations (which has $\alpha=1$), and even higher than for our variation with $\alpha=0.25$. Beyond this, the efficiency drop across metallicity is similar to the fiducial in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and in the change of formation channel for different period ranges across metallicity. We see the highest formation efficiency for variation $q3$. Only the shortest-period binaries do not form a DWD through mergers at higher metallicities. At low metallicities, we see that even binaries with very close ZAMS separations form He + He DWDs. We thus see a higher efficiency from F50 over FZ because of the higher number of shortest-period ZAMS binaries in the log-uniform distribution of F50.}

\snotes{For CO + He binaries, there are again many more mergers for $\alpha25$ relative to the fiducial case. This is the dominating way that binaries are lost at higher metallicities. At low metallicities we also see a number of systems form CO + CO binaries instead -- this is especially the case in a ``Goldilocks zone" around log$_{10}$(Z/Z$_\odot$)sim -2, where RLOF occurs late enough in evolution that mass transfer remains stable and CO + CO's are formed, hence why we see a dip in the formation efficiency. Because $\alpha5$ allows for less mergers due to the high CE efficiency, the formation efficiency is mostly governed by our metallicity-dependent orbital period distribution. At higher metallicities the majority of lost systems from mergers or from forming He + He binaries instead due to the faster evolution at high metallicities and increasing radii allowing for earlier interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?]. At higher metallicities, we also have the ZAMS orbital period distribution of FZ drops below the flat distribution for F50 and extends out to orbital periods beyond what would form a CO + He, thus the formation efficiencies for FZ and F50 cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$.}

\snotes{** still need to do q3 **, and all for CO + CO and ONe + X}

@@

Figure \ref{fig:CEsep} shows the average separation at the first instance of CE evolution, $a_{\text{CE}}$ of all DWD progenitors that result in systems orbiting in the LISA frequency band at present day, as a function of metallicity for each DWD type. The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading. \snotes{We show this for our fiducial model and two of the binary parameter variations. For our fiducial, $\alpha25$ and $\alpha5$ models,} the average CE separation increases in general across metallicity. Higher-metallicity binaries will interact earlier in the binary's lifetime than a lower-metallicity binary of equal separation due to their relatively larger maximum radii. Since higher-metallicity binaries are also more likely to merge during CE interactions because of their relatively more massive donor envelopes, the DWDs which survive and eventually orbit in the LISA band originate from systems with higher interaction separations which allow their orbits to shrink significantly during CE phases without merging. This regulation plays a key role in smearing out any observable effects of a metallicity-dependent binary fraction in the population of DWDs observable by LISA. \snotes{The slope of the increase for these three models is dictated by the CE efficiency $\alpha$. With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution [is this the first time this idea is introduced? need to check], requiring more orbital energy to be available in order to eject the CE. Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected. We thus see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial model which has $\alpha=1$.}
